Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-11 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed the last paragraph on metis' section.

A proof derivation reply by \Metis for a classic propositional logic
without equality include in the \TSTP file at least six different inferences rules. These are exactly the same six rules from the
\Metis's description in Fig.~\ref{fig:metis-inferences}. The aforementioned rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
Based on the scope of the problems (CPL) but also from the list of 6 inferences rules described on the \Metis' documentation, only 3 rules can be applied: \emph{axiom}, \emph{assume} and \emph{resolve}.

Comparing these rules with \TSTP derivations but also after looking at the
\Metis' source code, we speculate to say that for example.
The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} appears using the
same name with the binary rule \resolve. The \emph{assume} rule is the inference rule \negate to introduce the negation of the conjecture since
\Metis replies refutation proofs. The \strip rule works with the conjecture, also named as the \emph{goal} of the problem. This intends for finding a equivalent conjunction of easier or smaller in size propositions, named \emph{subgoals}.

This section briefly describes the \Metis prover for our purposes.
In the next section, we discuss the proof-reconstruction for \Metis \TSTP derivations. In addition, we show a more detailed discussion around
the aforementioned proof rules.

>>>>

A \TSTP proof derivation reply by \Metis for a classic propositional logic without equality can includes  at least six different inferences rules. These are not exactly the same rules showed in \Metis's description from the Fig.~\ref{fig:metis-inferences}. The observed rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
Based on the scope of the problems (CPL) but also from the \Metis' documentation, only 3 rules can be applied here: \emph{axiom}, \emph{assume} and \emph{resolve} rule.

Comparing these rules with \TSTP derivations and  after looking at the
\Metis' source code, we believe the rules in \TSTP derivations comes from the following explanation.
The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} rule appears using the
same name in the binary resolution rule, \resolve. The \emph{assume} rule is the inference rule \negate that introduces the negation of a conjecture, since \Metis replies refutation proofs. To end with the rules, we found the \strip rule. This one works only for conjectures. In \Metis, a conjecture is also named as the \emph{goal} of the problem. This rule intends to prove conjuncts from a equivalent conjunction of the goal. These conjuncts intends to split the goal into less complex propositions, not necessary smaller. These conjuncts are named \emph{subgoals}. At the end, a derivation is a proof of the goal, composed by proofs of each of these subgoals.

This section briefly describes the \Metis prover for our purposes.
In the next section, we discuss the proof-reconstruction for \Metis' \TSTP derivations. In addition, we show a more detailed discussion around
the aforementioned proof rules.
